Jesse Lu

### 2013-05-07 resume/cv.tex
New CV.

\section{Education}          
    Stanford University, PhD, Electrical Engineering, June 2013 (in progress) \\
    Stanford University, Masters of Science, Electrical Engineering, May 2012 \\
    University of California Los Angeles, Bachelor of Science, Electrical Engineering, June 2006

@@

\section{PhD Research: Nanophotonic computational design}
Developed software to 
    design arbitrary linear nanophotonic devices which 
    are fully three-dimensional and multi-modal,
    exhibit novel functionality,
    have very compact footprints,
    exhibit high efficiency, 
    are strongly robust to fluctuations in 
    wavelength, temperature and fabrication error, and
    are manufacturable.
Critically, the developed software 
    does not require the user to be a nanophotonic expert or 
    to perform any manual tuning. 
Instead, devices are designed
    solely based on the user's desired performance specification for the device.

@@

\section{Research Experience}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Graduate Researcher} \>Jelena Vuckovic Group \>2007-Present\\
                             \>Stanford University
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Existing nanophotonic design process consisted of trial-and-error
        where each simulation about 24 hours to complete.
    Implemented FDTD and FDFD simulation software on hardware-accelerated platforms 
    to bring simulation times down to 10 minutes.
    Also developed a novel ``objective-first'' nanophotonic design algorithm
        and demonstrated automated design of arbitrary linear nanophotonic 
        devices.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Undergraduate Researcher} \>Eli Yablonovitch Group \> 2005-2006\\
                          \>University of California, Los Angeles
   \end{tabbing}\vspace{-20pt}
    Surface plasmon focusing device required a grating coupler to inject energy
        into the surface plasmon mode.
    Wrote a Matlab program interfacing with a FEM package (COMSOL),
        developed a hierarchal optimization routine as well as an extended 
        transfer matrix model to produce first-ever thoroughly optimized 
        grating coupler design.

>>>>

\section{Education}          
    Stanford University, PhD, Electrical Engineering, June 2013 \\
    Stanford University, Masters of Science, Electrical Engineering, May 2012 \\
    University of California Los Angeles, Bachelor of Science, Electrical Engineering, June 2006

@@

\section{PhD Research: Nanophotonic Computational Design and Optimization}
\begin{itemize}
\item Nanophotonic design and optimization was 
    a brute force, trial-and-error process
    which took \emph{weeks to months} to improve a single structure---even with 
    a good initial guess.
\item I had to build a system to design structures within a day,
    solely based on the performance specification of the desired device,
    and without good initial guesses.
\item I applied methods from the field of convex optimization 
    to the physical problem of linear nanophotonic design. 
    I sped up computation by implementing my method on GPUs,
    and achieved scale by leveraging the cloud (Amazon EC2).
\item This resulted in the design 
    of nanophotonic devices that were either
    more compact, more robust, or more efficient 
    than all previous designs.
    Critically, these designs only required a day (or two) of computation,
    and a specification for the intended performance (no good initial guess).
    \end{itemize}

@@

\section{Research Experience}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Graduate Researcher} \>Jelena Vuckovic Group \>2007-Present\\
                             \>Stanford University
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
%   Existing nanophotonic design process consisted of trial-and-error
%       where each simulation about 24 hours to complete.
%   Implemented FDTD and FDFD simulation software on hardware-accelerated platforms 
%   to bring simulation times down to 10 minutes.
%   Also developed a novel ``objective-first'' nanophotonic design algorithm
%       and demonstrated automated design of arbitrary linear nanophotonic 
%       devices.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Undergraduate Researcher} \>Eli Yablonovitch Group \> 2005-2006\\
                          \>University of California, Los Angeles
   \end{tabbing}\vspace{-20pt}
%   Surface plasmon focusing device required a grating coupler to inject energy
%       into the surface plasmon mode.
%   Wrote a Matlab program interfacing with a FEM package (COMSOL),
%       developed a hierarchal optimization routine as well as an extended 
%       transfer matrix model to produce first-ever thoroughly optimized 
%       grating coupler design.
